On the application of microwave acoustic resonant viral inactivation \thanks{I would be delighted to include any criticisms or comments anyone may have; preferably leave them on the GitHub issues page, or email therobotist@gmail.com, @0xDBFB7 on Twitter, or irc.0xDBFB7.com:6667 \#covid.}

### 2020-09-08 documents/paper.tex
Bunch of simulations, bunch of garbage

@@

>>>>

Industry Canada limits on the instantaneous electric field anywhere inside the body are $1.35 \times 10^-4$ V/m * Hz ()\cite{RSS1022015}, Table 4), $0.81 \times 10^6$ V / m \@ 6 GHz to $1.2 \times 10^6$ / m \@ 9 GHz

6 cm of l

The

@@

Conduction effects. Because the transmission line voltage only goes as the to the square root of the input power

There seems to be some sort of focusing effect which makes internal bronchoscopic treatment slightly more effective than might be expected.
